[atmosfear_default_parameters]
opt_weather_balance_presets		= balance_default ;name of the global preset. Used only with in game options
opt_weather_length_presets		= length_default ;name of the global preset. Used only with in game options

;opt_$1_period_$2 				= $3  	definition of which weather graph section ($3) to use for certain area ($1) and period ($2)
;										graphs are defined in configs\environment\dynamic_weather_graphs.ltx
;										You can create your own sections if you need more variations. 
;										E.g. if you create new section called [atmosfear_misery_clear] use 'misery_clear' as value $3
;opt_$1_period_$2_length		= $3	length of the given period ($2) for the area ($1)
;										the minimum value is 3, maximum 12. Don't exceed those values as it may produce unexpected results.

opt_zaton_period_good			= clear_foggy 
opt_zaton_period_bad			= foggy_rainy
opt_zaton_period_good_length	= 3
opt_zaton_period_bad_length	= 16
opt_jupiter_period_good			= clear_foggy 
opt_jupiter_period_bad			= foggy_rainy
opt_jupiter_period_good_length	= 3
opt_jupiter_period_bad_length	= 3
opt_pripyat_period_good			= clear_foggy
opt_pripyat_period_bad			= rainy
opt_pripyat_period_good_length	= 4
opt_pripyat_period_bad_length	= 12

opt_enable_blowout				= 1				; 1 enables blowouts, 0 prevents blowouts from happening.
opt_blowout_freq				= 48 				; blowout frequency. Blowout happens every x/2 to x hours. Don't use value lower then 6h (every 3 to 6h).
opt_blowout_fate				= kill
opt_blowout_warning				= siren			; type of blowout warning. Possible settings: radio_siren, radio, siren, nowarning.
opt_blowout_task				= dontgive			; task to hide/stay in cover during blowouts. Possible settings: give, dontgive.
opt_enable_fallout				= 0			; 1 enables fallouts, 0 prevents fallouts from happening
opt_fallout_freq				= 48				; fallout frequency. Fallout happens every x/2 to x hours. Don't use value lower then 6h (every 3 to 6h) and odd numbers (e.g. 11)
opt_fallout_fate				= poison			; fate of NPCs during fallouts. Possible settings: poison, unhurt.
opt_fallout_warning				= siren				; type of fallout warning. Possible settings: siren, nowarning.
opt_fallout_task				= dontgive			; task to hide/stay in cover during fallouts. Possible settings: give, dontgive.
opt_enable_psi_storm				= 0				; 1 enables fallouts, 0 prevents fallouts from happening
opt_psi_storm_freq				= 48				; psi storm frequency. Psi storm happens every x/2 to x hours. Don't use value lower then 6h (every 3 to 6h)
opt_psi_storm_fate				= kill				; fate of NPCs during psi storms. Possible settings: kill, turntozombie, unhurt.
opt_psi_storm_warning				= siren				; type of psi storm warning. Possible settings: siren, nowarning.
opt_psi_storm_task				= dontgive				; task to hide/stay in cover during psi storms. Possible settings: give, dontgive.

opt_moon_phase					= 8days				; lenght of the moon month. Possible settings: 28days, 8days.
opt_night_brightness				= slight			; brightness of the nights. Possible settings: dark, slight, medium, bright.

opt_god_mode					= false				; god mode for all the events. If set to true actor can walk unhurt during blowouts, fallouts and psi storms. Use only for testing.

;############################################
;#				LIST OPTIONS
;############################################
[list_weather_balance_presets]
list_weather_balance_preset_default 	= 0
list_weather_balance_preset_good 		= 1
list_weather_balance_preset_bad 		= 2
list_weather_balance_preset_custom 		= 3

[list_weather_length_presets]
list_weather_length_preset_default 		= 0
list_weather_length_preset_short 		= 1
list_weather_length_preset_long 		= 2
list_weather_length_preset_custom 		= 3

[list_periods]
list_periods_clear = 0
list_periods_clear_foggy = 1
list_periods_foggy = 2
list_periods_foggy_rainy =3
list_periods_rainy = 4
list_periods_stormy = 5

[list_blowout_freq]
list_freq_12					= 0
list_freq_24					= 1
list_freq_48					= 2
list_freq_96					= 3

[list_blowout_fate]
list_fate_killatend				= 0
list_fate_killatwave			= 1
list_fate_turntozombie			= 2
list_fate_explode				= 3

[list_blowout_warning]
list_warning_radio_siren		= 0
list_warning_radio				= 1
list_warning_siren				= 2
list_warning_none				= 3

[list_blowout_task]
list_task_give = 0
list_task_none = 1

[list_fallout_freq]
list_freq_12					= 0
list_freq_24					= 1
list_freq_48					= 2
list_freq_96					= 3

[list_fallout_fate]
list_fate_poison = 0
list_fate_none = 1

[list_fallout_warning]
list_warning_siren = 0
list_warning_none = 1

[list_fallout_task]
list_task_give = 0
list_task_none = 1

[list_psi_storm_freq]
list_freq_12					= 0
list_freq_24					= 1
list_freq_48					= 2
list_freq_96					= 3

[list_psi_storm_fate]
list_fate_kill = 0
list_fate_turntozombie = 1
list_fate_none = 2

[list_psi_storm_warning]
list_warning_siren = 0
list_warning_none = 1

[list_psi_storm_task]
list_task_give = 0
list_task_none = 1

[list_night_brightness]
list_night_brightness_dark = 0
list_night_brightness_slight = 1
list_night_brightness_medium = 2
list_night_brightness_bright = 3

;############################################
;#				PRESETS
;############################################
[atmosfear_preset_balance_default]
zaton_period_good			= clear_foggy
zaton_period_bad			= rainy
jupiter_period_good			= clear
jupiter_period_bad			= foggy_rainy
pripyat_period_good			= clear_foggy
pripyat_period_bad			= stormy

[atmosfear_preset_balance_good]
zaton_period_good			= clear
zaton_period_bad			= foggy_rainy
jupiter_period_good			= clear
jupiter_period_bad			= foggy_rainy
pripyat_period_good			= clear
pripyat_period_bad			= foggy_rainy

[atmosfear_preset_balance_bad]
zaton_period_good			= clear_foggy
zaton_period_bad			= stormy
jupiter_period_good			= clear_foggy
jupiter_period_bad			= stormy
pripyat_period_good			= clear_foggy
pripyat_period_bad			= stormy

[atmosfear_preset_length_default]
zaton_period_good_length	= 6
zaton_period_bad_length		= 6
jupiter_period_good_length	= 8
jupiter_period_bad_length	= 4
pripyat_period_good_length	= 4
pripyat_period_bad_length	= 8

[atmosfear_preset_length_short]
zaton_period_good_length	= 3
zaton_period_bad_length		= 3
jupiter_period_good_length	= 3
jupiter_period_bad_length	= 3
pripyat_period_good_length	= 3
pripyat_period_bad_length	= 3

[atmosfear_preset_length_long]
zaton_period_good_length	= 12
zaton_period_bad_length		= 12
jupiter_period_good_length	= 12
jupiter_period_bad_length	= 12
pripyat_period_good_length	= 12
pripyat_period_bad_length	= 12

;############################################
;#				OPTION NAMES
;############################################
[atmosfear_option_names]
balance_default	= st_list_weather_balance_preset_default
balance_good	= st_list_weather_balance_preset_good
balance_bad		= st_list_weather_balance_preset_bad
balance_custom	= st_list_weather_balance_preset_custom
length_default	= st_list_weather_length_preset_default
length_short	= st_list_weather_length_preset_short
length_long		= st_list_weather_length_preset_long
length_custom	= st_list_weather_length_preset_custom

clear			= st_list_periods_clear
clear_foggy		= st_list_periods_clear_foggy
foggy			= st_list_periods_foggy
foggy_rainy		= st_list_periods_foggy_rainy
rainy			= st_list_periods_rainy
stormy			= st_list_periods_stormy

killatend		= st_list_fate_killatend
killatwave		= st_list_fate_killatwave
turntozombie 	= st_list_fate_turntozombie
explode			= st_list_fate_explode
poison 			= st_list_fate_poison
unhurt			= st_list_fate_none
kill			= st_list_fate_kill
killorturn		= st_list_fate_killorturn
radio_siren		= st_list_warning_radio_siren
radio			= st_list_warning_radio
siren			= st_list_warning_siren
nowarning		= st_list_warning_none
give			= st_list_task_give
dontgive		= st_list_task_none

dark 			= st_list_night_brightness_dark
slight			= st_list_night_brightness_slight
medium			= st_list_night_brightness_medium
bright			= st_list_night_brightness_bright

12				= st_list_freq_12
24				= st_list_freq_24
48				= st_list_freq_48
96				= st_list_freq_96



